### 2023-11-07 Notes/optest_update.tex
Added simulations with optimal delta estimator.

\[ \frac{I(C = \infty) g(Z)}{\varpi(\infty, Z)} + \frac{I(C =
  \infty)}{\varpi(\infty, Z)} \left(\sum_{r \neq \infty} \varpi(r, G_r(Z))
  L_{2r}(G_r(Z))\right) - \sum_{r \neq \infty} I(C = \infty)L_{2r}(G_r(Z))\]

@@

It turns out that $\hat \theta_{prop}$ from Equation~\ref{eq:prop} is contained within 
the previous class of estimators with

\[L_{2r}(G_r(Z)) = \varpi(r, G_r(Z)) E[g(Z) \mid G_r(Z)].\]

(See pages 81-82 of notes for proof.) \\

@@

The goal is now to find the coefficients $c_0, c_1$, and $c_2$ such that 
$\langle \hat \theta_c, L_2\rangle \equiv E[\hat \theta_c L_2] = 0$ for 
all $L_2 \in \Lambda_2$ (see \cite{tsiatis2006semiparametric} for definition 
of $\Lambda_2$). If we can find such coefficients that the estimator $\hat
\theta_c$ will be orthogonal to $\Lambda_2$ and hence by Theorem 10.1 of 
\cite{tsiatis2006semiparametric} semiparametrically optimal. The good news 
is that we know (CITEME) that any element $L_2 \in \Lambda_2$ has a form:

@@

\subsection*{Optimal Normal Model}

An alternative optimization problem is to find coefficients $c_0$, $c_1$, and
$c_2$, that minimize the variance of $\hat \theta_c$. After expanding the 
variance and differentiating by each $c_i$, the optimal parameters are

@@

>>>>

\begin{equation}\label{lambda2}
 \frac{I(C = \infty) g(Z)}{\varpi(\infty, Z)} + \frac{I(C =
  \infty)}{\varpi(\infty, Z)} \left(\sum_{r \neq \infty} \varpi(r, G_r(Z))
  L_{2r}(G_r(Z))\right) - \sum_{r \neq \infty} I(C = r)L_{2r}(G_r(Z))
\end{equation}

@@

%It turns out that $\hat \theta_{prop}$ from Equation~\ref{eq:prop} is contained within 
%the previous class of estimators with 
%
%\[L_{2r}(G_r(Z)) = \varpi(r, G_r(Z)) E[g(Z) \mid G_r(Z)].\]
%
%(See pages 81-82 of notes for proof.) \\

@@

The goal is now to find the coefficients $c_0, c_1$, and $c_2$ such that 
$\langle \hat \theta_c, L_2\rangle \equiv E[\hat \theta_c L_2] = 0$ for 
all $L_2 \in \Lambda_2$ (see \cite{tsiatis2006semiparametric} for definition 
of $\Lambda_2$). If we can find such coefficients that the estimator $\hat
\theta_c$ will be orthogonal to $\Lambda_2$ and hence by Theorem 10.1 of 
\cite{tsiatis2006semiparametric} semiparametrically optimal. The good news 
is that we know (from Theorem 7.2) that any element $L_2 \in \Lambda_2$ has a
form:

@@

\subsection*{Optimal Model}

Due to the fact that I do not know how to solve the previous equations, there 
is another way to construct an optimal model. We can find the values of 
$c_0$, $c_1$, and $c_2$ in $\hat \theta_c$ that minimize the variance the 
estimator. We can find these values by differentiating by $c_i$ and solving 
for $c_i$:

@@

This estimator is similar to several other estimators:

\begin{align}\label{thetaind}
  \hat \theta^{ind}_c 
  &= \frac{\delta_{11}}{\pi_{11}} g(Z) + \left(1 -
    \left(\frac{\delta_{10}}{\pi_{10}}\right) -
    \left(\frac{\delta_{01}}{\pi_{01}}\right) + 
  \frac{\delta_{11}}{\pi_{11}}\right) c_0 E[g \mid X] \\ \nonumber
  &+
  \left(\frac{\delta_{10}}{\pi_{10}} - 
  \frac{\delta_{11}}{\pi_{11}}\right) c_1 E[g \mid X, Y_1] +
  \left(\frac{\delta_{01}}{\pi_{01}} - 
  \frac{\delta_{11}}{\pi_{11}}\right) c_2 E[g \mid X, Y_2]
\end{align}

\begin{align}\label{thetadelta}
  \hat \theta^{\delta}_c 
  &= \frac{\delta_{11}}{\pi_{11}} g(Z) 
  + \left(\frac{\delta_{11}}{\pi_{11}} - \frac{\delta_{00}}{\pi_{00}}\right) 
   c_0 E[g \mid X] \\ \nonumber
  &+
  \left(\frac{\delta_{11}}{\pi_{11}} - 
  \frac{\delta_{10}}{\pi_{10}}\right) c_1 E[g \mid X, Y_1] +
  \left(\frac{\delta_{11}}{\pi_{11}} - 
  \frac{\delta_{01}}{\pi_{01}}\right) c_2 E[g \mid X, Y_2]
\end{align}

The first expression (Equation~\ref{thetaind}) is the proposed estimator 
with independent differences in each segment, while the second expression 
(Equation~\ref{thetadelta}) is the optimal estimator with values of $\delta$
such that $\hat \theta^{\delta}_c \in \Lambda_2$, which means that it has 
the form of the semiparametric in Equation~\ref{lambda2}.
